Geometric models overestimate lake depth due to imperfect slope measurement

### 2020-12-03 manuscript/agujournaltemplate.tex
text edits

\begin{keypoints}
\item Geometric models to predict lake depth, which require in-lake slope, assume that nearshore land slope is a good proxy for in-lake slope.
\item Using data from thousands of lakes, we show that nearshore land slope is a poor proxy for in-lake slope and increases prediction error.
\item Prediction errors were systematic such that depth was overpredicted in concave and reservoir lakes.
\end{keypoints}

@@

\subsection{Future research}
\noindent
One of our models (true slope, proxy distance) was more accurate than even the most accurate of prior studies. However, parameterization of this model requires data on bathymetry which is not available for all lakes. We propose that the error rate of this model ($\pm$ 4.4m, 29\%) be used as an out-of-sample prediction benchmark for future studies such that they should attempt to match it but not expect to exceed it.

>>>>

\begin{keypoints}
\item Geometric models to predict lake depth, which require in-lake slope, assume that nearshore land slope is a good proxy for in-lake slope.
\item Using data from thousands of lakes, we show that nearshore land slope is a poor proxy for in-lake slope and increases prediction error.
\item Systematic overprediction of depth in concave and reservoir lakes highlights the potential for improvement in future depth prediction efforts.
\end{keypoints}

@@

\subsection{Future research}
\noindent
One of our models (where $depth_{geometric}$ was calculated using true slope and proxy distance) was more accurate than even the most accurate of prior studies. However, parameterization of this model requires data on bathymetry which is not available for all lakes. We propose that the error rate of this model ($\pm$ 4.4m, 29\%) be used as an out-of-sample prediction benchmark for future studies such that they should attempt to match it but not expect to exceed it.
